---
params:
  title: "02_exploratory_data_analysis"
  participant_id: 1
  visualize: TRUE
title: '`r stringr::str_c(stringr::str_to_title(params$title), " - participant ", params$participant_id)`'
author: "Bram Zandbelt"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    number_sections: true
    df_print: paged
    code_folding: hide
    theme: readable
    highlight: pygments
    bibliography: "cmdsddfeitc.bib"
    biblio-style: author-year
---

```{r setup, include=FALSE}
# Set root dir to project directory to ensure that code is always run relative to the project directory, no matter if it is run using `knitr` or interactively.
knitr::opts_knit$set(root.dir = rprojroot::find_root(rprojroot::has_file("DESCRIPTION")))

# Attach tideverse package to enable access to pipe (%>%)
require(tidyverse)
```

# Overview


# Preliminaries

Before reading the data the following is specified:

```{r Define notebook name, based on YAML header}
notebook_name <- 
   stringr::str_to_lower(stringr::str_replace_all(params$title, " ", "_"))
```
- the _name of the notebook (`notebook_name`)_, which is used to save output to a notebook-specific directory

```{r Define relevant directories for reading and writing data and create whenever needed}
# Raw trial log files are read from here
preprocessed_data_dir <- 
  file.path("data","derivatives", "01_preprocessing", "included")

# Derivatives will be written here
eda_dir <- 
  file.path("data","derivatives", notebook_name)

# Create non-existing dirs if they don't exist
cmdsddfeitc::check_dir(all_dirs = c(preprocessed_data_dir, eda_dir))

```
- all _relevant directories_ for reading and writing data

```{r File name and task version}
# Determine which file should be read
expt_standard_trials_filename <- list.files(path = preprocessed_data_dir, 
                                            pattern = sprintf("^experiment_standard_trials_.*%.3d.csv$",
                                                              params$participant_id[[1]])
                                            )

# Determine task version, because factor levels (e.g. framing, trial_type) are task-dependent
task_version <- ifelse(stringr::str_detect(expt_standard_trials_filename, "defer_speedup"),
                    "defer_speedup",
                    ifelse(stringr::str_detect(expt_standard_trials_filename, "date_delay"),
                           "date_delay",
                           NA
                           )
                    )
```
- the _filename of the trial log file (`trial_log_filename`)_ and _task version (`task_version`)_

# Read data

Having specified all relevant variables, the cleaned standard trials from the experiment are read:
```{r Read trial_log data, warning=FALSE}
# Read (and print) the data, using task-dependent column specifications
(expt_trials <-
    readr::read_csv(file = file.path(preprocessed_data_dir, expt_standard_trials_filename),
                    col_types = cmdsddfeitc::get_col_types(stringr::str_c("expt_standard_trials_",
                                                                          task_version)))
  )
```

# Preprocess data
```{r Choice proportions}
choice_props <- 
  expt_trials %>%
  dplyr::mutate(t_l = factor(t_l, levels = c(2,4,8,16,32,64,128))) %>%
  dplyr::group_by(frame, t_l, m_s_cat) %>%
  dplyr::summarize(p_ll = sum(choice == "ll") / n(),
                   m_s = median(m_s))

```

```{r}
choice_pctgs <- 
  expt_trials %>%
  dplyr::group_by(frame, choice) %>%
  dplyr::summarize (n = n()) %>%
  dplyr::mutate(percentage = n / sum(n))

choice_pctgs

```

Response time data
```{r}
rt_data <- 
  expt_trials %>%
  dplyr::mutate(t_l = factor(t_l, levels = c(2,4,8,16,32,64,128)),
                m_s_cat = factor(m_s_cat, 
                                 levels = c("below_ip", "at_ip", "above_ip"),
                                 labels = c("-", "at", "+"))
                )
```


# Analyze data


# Visualize data

Visualize how choice percentages vary between frames

```{r Plot distribution of choices between frames, out.width="100%"}
if (params$visualize) {
 ggplot2::ggplot(choice_pctgs,
                ggplot2::aes(x = frame,
                             y = percentage,
                             fill = choice)) + 
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::geom_text(ggplot2::aes(label = paste0(round(100*percentage),"%")),
                     position = position_stack((vjust = 0.5)),
                     color = "white") +
  ggplot2::scale_x_discrete(name = "Frame") + 
  ggplot2::scale_y_continuous(name = "Cumulative choice proportion") + 
  ggplot2::scale_fill_manual(values = c("red", "navy")) + 
  ggplot2::ggtitle("Distribution of choices between frames") +
  ggplot2::coord_flip() + 
  ggplot2::theme_minimal() + 
  ggplot2::theme(panel.grid = ggplot2::element_blank()) 
}
```

Visualize how choice proportions vary between SS amount, delays (colors), and frames (panels)

Choice proportions across amounts, delays, and frames
```{r Plot probability of choosing LL option as a function of SS offer across delays and frames, out.width="100%"}
if (params$visualize) {
 ggplot2::ggplot(data = choice_props,
                ggplot2::aes(x = m_s,
                             y = p_ll,
                             group = t_l,
                             color = t_l)
                ) +
  ggplot2::facet_wrap("frame", ncol = 1) + 
  ggplot2::geom_point(shape = 21,
                      stroke = 1) + 
  ggplot2::scale_color_viridis_d(name = "Delay (days)") + 
  # ggplot2::scale_color_brewer(name = "Delay (days)",
  #                             palette = "Set2") + 
  ggplot2::scale_x_continuous(name = "Smaller-sooner amount (€)",
                              limits = c(0, 43.52)) +
  ggplot2::scale_y_continuous(name = "Probability of choosing larger-later option",
                              limits = c(0, 1)) +
  
  ggplot2::ggtitle("P(LL choice | SS amount, delay, frame)") +
  ggplot2::theme_minimal() + 
  ggplot2::theme(panel.grid = ggplot2::element_blank(),
                 panel.background = ggplot2::element_rect(fill = "gray95",color = NA),
                 aspect.ratio = 1/1.61) 
}
```

Visualize how response times vary between frames, delays (columns), and SS amount categories (rows)

```{r Plot response times as a function of frame, delay, and SS amount category, out.width="100%"}
if (params$visualize) {
 ggplot2::ggplot(rt_data,
                ggplot2::aes(x = frame,
                             y = rt,
                             color = choice)) +
  ggplot2::facet_grid(m_s_cat ~ t_l) + 
  ggplot2::geom_hline(yintercept = 1.5, linetype = "dashed") +
  ggplot2::geom_hline(yintercept = 10, linetype = "dashed") +
  ggplot2::geom_point(shape = 21,
                      stroke = 1) +
  ggplot2::scale_x_discrete(name = "Frame") +
  ggplot2::scale_y_continuous(name = "Response time (s)",
                              breaks = c(2, 5, 8),
                              limits = c(0,10)) +
  ggplot2::scale_color_discrete(name = "Choice") +
  ggplot2::ggtitle("RT across frames, delays, SS amount") +
  ggplot2::coord_flip() +
  
  cmdsddfeitc::theme_cmfsddfeitc() + 
  ggplot2::theme(legend.position = "bottom") 
}
```

# Write data

Choice proportions
```{r Write choice proportion data to disk}
# Add relevant variables, so that these files can be read and combined into a larger data frame for additional analysis
choice_props <- 
  choice_props %>%
  dplyr::mutate(participant_id = params$participant_id) %>%
  dplyr::select(participant_id, dplyr::everything())

# Make file name human- and machine-readable, so that main results can be read from file name
choice_props_file <- 
  file.path(eda_dir,
            sprintf("choice_proportions_task-%s_pid-%.3d.csv",
                    task_version,
                    params$participant_id # pid
                    )
            )

readr::write_csv(choice_props,
                 path = choice_props_file
            )
print(sprintf("%s", choice_props_file))
```

Choice percentages
```{r Write choice percentage data to disk}
# Add relevant variables, so that these files can be read and combined into a larger data frame for additional analysis
choice_pctgs <- 
  choice_pctgs %>%
  dplyr::mutate(participant_id = params$participant_id) %>%
  dplyr::select(participant_id, dplyr::everything())

# Make file name human- and machine-readable, so that main results can be read from file name
choice_pctgs_file <-
  file.path(eda_dir,
            sprintf("choice_percentages_task-%s_pid-%.3d.csv",
                    task_version,
                    params$participant_id # pid
                    )
            )
  
readr::write_csv(choice_pctgs,
                 path = choice_pctgs_file
            )
print(sprintf("%s", choice_pctgs_file))
```


Note: The RT data will not be written to disk, because they would be identical to the `expt_trials` read from disk in this notebook.
